Glyph-maps for Visualizing Climate Data and Models

### 2011-09-29 paper.tex
Fix aspect ratio of USHCN plots to match GISTEMP plots
typos

Climate data poses visual challenges because it is has both spatial and temporal components, and is often multivariate. In this paper we propose an new display for climate data: glyph-maps. Glyph-maps are a specialization of multivariate glyph plots; each spatial location is displayed with one glyph that represents the measurements recorded over time at that location. Glyph-maps allow the discovery of both local and global structure, with a particular focus on temporal relationships.

@@

  \caption{Glyph-map of predicted temperature anomaly data (GISTEMP), from
    1950-2010. Increasing trends can be seen over most of the USA,
    with varying degrees of increase. Some isolated locations exhibit
    steep declines, and inclines, perhaps indicative of some isolated
    data problems. References line are straight, but look curves because of
    the Z\"ollner optical illusion}
  \label{fig:gistemp-pred}
\end{figure}

>>>>

Understanding the multiple aspects of climate data is a challenge. There are both spatial and temporal components to examine, and often multivariate dependencies. In this paper we propose a new display for climate data: glyph-maps. Glyph-maps are a specialization of multivariate glyph plots; each spatial location is displayed with one glyph that represents the measurements recorded over time at that location. Glyph-maps allow the discovery of both local and global structure, with a particular focus on temporal relationships.

@@

  \caption{Glyph-map of predicted temperature anomaly data (GISTEMP),
    from 1950-2010. Increasing trends can be seen over most of the
    USA, with varying degrees of increase. Some isolated locations
    exhibit steep declines, and inclines, perhaps indicative of some
    isolated data problems. Note that, the reference lines are
    straight, but they look curved because of the Z\"ollner optical
    illusion.}
  \label{fig:gistemp-pred}
\end{figure}
